Dominance Regions for Rank Two Cluster Algebras

### 2022-04-04 dominance_regions.tex
Some reorganization -- not finished

  When $bc\le3$, the cluster algebra $\cA(b,c)$ will be of finite-type and cluster monomials form its only pointed basis.
  We will therefore assume that $bc\ge4$.
  In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
  Specifically, we show that the $\bfg$-vector $\lambda$ dominates precisely the collection of $\lambda+(b\ZZ\oplus c\ZZ)$-lattice points in its \emph{dominance polygon} $\cP(\lambda)$.
  Specifically, we show that the $\bfg$-vector $\lambda$ dominates precisely the collection of $\bfg$-vectors of the form $\lambda+(b a_1 ,c a_2)$ inside its \emph{dominance polygon} for integers $a_1,a_2$.
  %In this case, we compute the possible transitions between any two pointed bases.
  %The collection of $\bfg$-vectors which can appear in the deformation of a pointed basis is the \emph{dominance region}.
  \begin{theorem}
    The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
    {
      \everymath={\displaystyle}
      \def\arraystretch{2.8}
      \[
        \begin{array}{rcccl}
          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
          \\
          \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \leq & 0
          \\
          0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
          \\
          \min\left(b \lambda_2,0\right) & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) & \leq & 0
        \end{array}
      \]
    }
  \end{theorem}

@@

  \begin{theorem}
    There are six classes of dominance polytopes.
    \begin{enumerate}
      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cP(\lambda)$ is the point $\lambda$. 
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_1-b\lambda_2,c\lambda_1+2\lambda_2\big)$.
      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$.
      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_1+b\lambda_2,-c\lambda_1-(bc-2)\lambda_2\big)$.
    \end{enumerate}
  \end{theorem}

@@

  Given a Laurent polynomial in $\ZZ[x_1^{\pm1},x_2^{\pm1}]$, its \emph{support} is the set of its exponent vectors inside $\ZZ^2$.
  \begin{theorem}
    For a $\bfg$-vector $\lambda=(\lambda_1,\lambda_2)\in\ZZ^2$ the support for a pointed basis vector $x_\lambda$ is contained in the (possibly degenerate) lattice quadrilateral $\cS_\lambda$ given as follows:
    \begin{enumerate}
      \item If $\lambda$ lies outside of $\cI$, there are the following possibilities:
        \begin{enumerate}
          \item If $0\le\lambda_1,\lambda_2$, then $\cS_\lambda$ is just the point $\lambda$.
          \item If $\lambda_2 < 0$ and $0\le\lambda_1+b\lambda_2$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_1+b\lambda_2,\lambda_2)$.
          \item If $\lambda_1 < 0$ and $0\le\lambda_2$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_1,-c\lambda_1+\lambda_2)$.
          \item If $\lambda_1,\lambda_2 < 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $(\lambda_1,-c\lambda_1+\lambda_2)$.
          \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $-c\lambda_1-(bc-1)\lambda_2\le 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $\big((bc+1)\lambda_1-b^2c\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$.
          \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $0 < -c\lambda_1-(bc-1)\lambda_2$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $(0,0)$.
        \end{enumerate}
      \item If $\lambda$ lies inside of $\cI$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_1+b\lambda_2,-c\lambda_1-(bc-2)\lambda_2\big)$.
    \end{enumerate}
  \end{theorem}
    \newcommand{\boundingrays}{
      \tikzmath{\b = 2; \c = 2.1; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
      \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -6; \ymax = 6;}
      \draw [color=lightgray, thick] (\xmin,0) -- (\xmax,0);
      \draw [color=lightgray, thick] (0,\ymin) -- (0,\ymax);
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax / \b);
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \c / \bcmo );
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \bcms / 2 / \b); 
      \draw [color=lightgray, thick] (0,0) -- ( - 2 * \b * \ymin / \bcps, \ymin); 
  \begin{tikzpicture}[scale=.3]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (\l,\l) circle (6pt);
    \begin{scope}[shift={(13,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (\l *\b + \l, - \l)  circle (6pt);
      \draw [very thick] (\l * \b + \l, -\l) -- (\l,-\l);
    \begin{scope}[shift={(26,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (-\l, \l)  circle (6pt);
      \draw [very thick] (-\l, \l) -- (-\l,\l + \l*\c);
    \begin{scope}[shift={(39, 0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (-\l, -\l)  circle (6pt);
      \draw [very thick] (-\l, -\l) -- (-\l - \l *\b, -\l) -- (-\l - \l*\b, \l*\c + \l*\b * \c -\l) -- (-\l, \l*\c -\l) -- cycle;
    \begin{scope}[shift={(0,-13)}]
      \boundingrays;
      \tikzmath{ \l = 3; \x = \b * \l - \l / 2 / \c; \y = -\l; }
      \fill (\b * \l - \l / 2 / \c , -\l)  circle (6pt);
      \draw [very thick] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
    \begin{scope}[shift={(13,-13)}]
      \boundingrays;
      \tikzmath{ \l = 2; \x = \b * \l - \l / 2 / \c; \y = -\l - 3*\l/10;}
      \fill (\x,\y)  circle (6pt);
      \draw [very thick] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  cycle;
    \begin{scope}[shift={(26,-13)}]
      \boundingrays;
      \tikzmath{ \l = 2; \x = \l/2/\c; \y = -\l; }
      \fill (\l / 2 / \c , -\l)  circle (6pt);
      \draw [very thick] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  cycle;
    \begin{scope}[shift={(39,-13)}]
      \boundingrays;
      \tikzmath{ \l = 3; \x = \c*\l/\b/1.03; \y = -\l; }
      \fill (\x , \y)  circle (6pt);
      \draw [very thick] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  cycle;

@@

  \begin{theorem}
    For $\lambda\in\cI\cap\ZZ^2$, there are five classes of dominance polytopes.
    \begin{enumerate}
      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and ???.
      \item if $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0)$, and $(0,\frac{\sqrt{bc(bc-4)}}{b}\ell)$.
      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$.
      \item if $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell)$.
      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and ???.
    \end{enumerate}
  \end{theorem}
  \begin{proof}
    Following Lemma~\ref{le:one direction}, we see that the intersection $\cP_+(\lambda)\cap\cP_-(\lambda)$ degenerates to a triangle precisely when
    \[\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\]
    or 
    \[\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2=-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2.\]
    The first equations reduces to $c\lambda_1+2\lambda_2=0$, while the second reduces to $2\lambda_1+b\lambda_2=0$.
    In particular, the rays spanned by $(2,-c)$ and $(b,-2)$ determine this change of state in the dominance regions $\cP(\lambda)$.
  \end{proof}

@@

  \begin{theorem}\label{th:Newton polygons}\cite[Proposition~4.1]{LLZ}, \cite[Corollary~3.5]{LLZ2}
  For $(a_1,a_2)\in\ZZ^2$, the smallest (possibly degenerate) lattice quadrilateral $R_{a_1,a_2}$ containing the support of $x[a_1,a_2]$ is determined as follows.
  \begin{enumerate}
    \item If $a_1 \leq 0$ and $a_2 \leq 0$, then $R_{a_1,a_2} = \{(-a_1,-a_2)\}$.
    \item If $a_1 \leq 0 < a_2$, then $R_{a_1,a_2} = \{(p_1,-a_2): -a_1\leq p_1\leq -a_1+ba_2\}$.
    \item If $a_2 \leq 0 < a_1$, then $R_{a_1,a_2} = \{(-a_1,p_2): -a_2 \leq p_2 \leq -a_2+ca_1\}$.
    \item If $0<ba_2\leq a_1$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1+ba_2,\; -a_2\le p_2\le -a_2-cp_1\right\}$.
    \item If $0<ca_1\leq a_2$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1-bp_2,\; -a_2\le p_2\le -a_2+ca_1\right\}$.
    \item If $0 < a_1 < ba_2$ and $0 < a_2 < ca_1$, then
    $$\aligned
    R_{a_1,a_2}=&\bigg\{(p_1,p_2)\bigg|\; -a_1\le p_1<0,\; -a_2\le p_2<\Big(\frac{a_2}{a_1}-c\Big)p_1\bigg\}\\
    &\bigcup\bigg\{(p_1,p_2): -a_1\le p_1<\Big(\frac{a_1}{a_2}-b\Big)p_2,\; -a_2\le p_2<0\bigg\}\\
    &\hspace{1.35em}\bigcup\Big\{(-a_1+ba_2,-a_2),(-a_1,-a_2+ca_1)\Big\}.
    \endaligned
    $$
  \end{enumerate}
  Moreover, if $z\in\cA(b,c)$ is pointed at $(a_1,a_2)$ with support contained in $R_{a_1,a_2}$, then $z=x[a_1,a_2]$. 
\end{theorem}
  \subsection{Deformation Support}
  The greedy basis of Lee, Li, and Zelevinsky \cite{lee-li-zelevinsky} can be defined as the positive pointed basis with minimal support.
  Here we identify the maximum possible support of its deformations.

>>>>

  When $bc\le3$, the cluster algebra $\cA(b,c)$ will be of finite-type and cluster monomials form its only pointed basis.
  We will therefore assume that $bc\ge4$.
  In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
  Specifically, we show that the $\bfg$-vector $\lambda$ dominates precisely the collection of $\lambda+(b\ZZ\oplus c\ZZ)$-lattice points in its \emph{dominance polygon} $\cP(\lambda)$.
  Specifically, we show that the $\bfg$-vector $\lambda$ dominates precisely the collection of $\bfg$-vectors of the form $\lambda+(b a_1 ,c a_2)$ inside its \emph{dominance polygon} for integers $a_1,a_2$.
  %In this case, we compute the possible transitions between any two pointed bases.
  %The collection of $\bfg$-vectors which can appear in the deformation of a pointed basis is the \emph{dominance region}.
  \begin{theorem}
    \label{th:dominance inequalities}
    The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
    {
      \everymath={\displaystyle}
      \def\arraystretch{2.8}
      \[
        \begin{array}{rcccl}
          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
          \\
          \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \leq & 0
          \\
          0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
          \\
          \min\left(b \lambda_2,0\right) & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) & \leq & 0
        \end{array}
      \]
    }
  \end{theorem}

@@

  \begin{theorem}
    \label{th:dominance vertices}
    There are six classes of dominance polytopes.
    \begin{enumerate}
      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cP(\lambda)$ is the point $\lambda$. 
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_1-b\lambda_2,c\lambda_1+2\lambda_2\big)$.
      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$.
      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_1+b\lambda_2,-c\lambda_1-(bc-2)\lambda_2\big)$.
    \end{enumerate}
  \end{theorem}

@@

  Given a Laurent polynomial in $\ZZ[x_1^{\pm1},x_2^{\pm1}]$, its \emph{support} is the set of its exponent vectors inside $\ZZ^2$.
  \begin{theorem}
    \label{th:maximum support}
    For a $\bfg$-vector $\lambda=(\lambda_1,\lambda_2)\in\ZZ^2$ the support for a pointed basis vector $x_\lambda$ is contained in the (possibly degenerate) lattice quadrilateral $\cS_\lambda$ given as follows:
    \begin{enumerate}
      \item If $\lambda$ lies outside of $\cI$, there are the following possibilities:
        \begin{enumerate}
          \item If $0\le\lambda_1,\lambda_2$, then $\cS_\lambda$ is just the point $\lambda$.
          \item If $\lambda_2 < 0$ and $0\le\lambda_1+b\lambda_2$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_1+b\lambda_2,\lambda_2)$.
          \item If $\lambda_1 < 0$ and $0\le\lambda_2$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_1,-c\lambda_1+\lambda_2)$.
          \item If $\lambda_1,\lambda_2 < 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $(\lambda_1,-c\lambda_1+\lambda_2)$.
          \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $-c\lambda_1-(bc-1)\lambda_2\le 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $\big((bc+1)\lambda_1-b^2c\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$.
          \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $0 < -c\lambda_1-(bc-1)\lambda_2$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $(0,0)$.
        \end{enumerate}
      \item If $\lambda$ lies inside of $\cI$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_1+b\lambda_2,-c\lambda_1-(bc-2)\lambda_2\big)$.
    \end{enumerate}
  \end{theorem}

\begin{figure}[h!]
  \centering
    \newcommand{\boundingrays}{
      \tikzmath{\b = 2; \c = 2.1; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
      \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -6; \ymax = 6;}
      \draw [color=lightgray, thick] (\xmin,0) -- (\xmax,0);
      \draw [color=lightgray, thick] (0,\ymin) -- (0,\ymax);
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax / \b);
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \c / \bcmo );
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \bcms / 2 / \b); 
      \draw [color=lightgray, thick] (0,0) -- ( - 2 * \b * \ymin / \bcps, \ymin); 
    }
  \begin{tikzpicture}[scale=.3]
    \begin{scope}[shift={(0,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (\l,\l) circle (6pt);
    \end{scope}
    \begin{scope}[shift={(13,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (\l *\b + \l, - \l)  circle (6pt);
      \draw [very thick] (\l * \b + \l, -\l) -- (\l,-\l);
    \end{scope}
    \begin{scope}[shift={(26,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (-\l, \l)  circle (6pt);
      \draw [very thick] (-\l, \l) -- (-\l,\l + \l*\c);
    \end{scope}
    \begin{scope}[shift={(39, 0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (-\l, -\l)  circle (6pt);
      \draw [very thick] (-\l, -\l) -- (-\l - \l *\b, -\l) -- (-\l - \l*\b, \l*\c + \l*\b * \c -\l) -- (-\l, \l*\c -\l) -- cycle;
    \end{scope}
    \begin{scope}[shift={(0,-13)}]
      \boundingrays;
      \tikzmath{ \l = 3; \x = \b * \l - \l / 2 / \c; \y = -\l; }
      \fill (\b * \l - \l / 2 / \c , -\l)  circle (6pt);
      \draw [very thick] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
    \end{scope}
    \begin{scope}[shift={(13,-13)}]
      \boundingrays;
      \tikzmath{ \l = 2; \x = \b * \l - \l / 2 / \c; \y = -\l - 3*\l/10;}
      \fill (\x,\y)  circle (6pt);
      \draw [very thick] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  cycle;
    \end{scope}
    \begin{scope}[shift={(26,-13)}]
      \boundingrays;
      \tikzmath{ \l = 2; \x = \l/2/\c; \y = -\l; }
      \fill (\l / 2 / \c , -\l)  circle (6pt);
      \draw [very thick] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  cycle;
    \end{scope}
    \begin{scope}[shift={(39,-13)}]
      \boundingrays;
      \tikzmath{ \l = 3; \x = \c*\l/\b/1.03; \y = -\l; }
      \fill (\x , \y)  circle (6pt);
      \draw [very thick] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  cycle;
    \end{scope}
  \end{tikzpicture}
\end{figure}

@@

  \begin{theorem}
    There are six classes of dominance polytopes.
    \begin{enumerate}
      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cP(\lambda)$ is the point $\lambda$. 
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_1-b\lambda_2,c\lambda_1+2\lambda_2\big)$.
      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$.
      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_1+b\lambda_2,-c\lambda_1-(bc-2)\lambda_2\big)$.
    \end{enumerate}
  \end{theorem}
  \begin{proof}
    Following Lemma~\ref{le:one direction}, we see that the intersection $\cP_+(\lambda)\cap\cP_-(\lambda)$ degenerates to a triangle precisely when
    \[\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\]
    or 
    \[\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2=-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2.\]
    The first equations reduces to $c\lambda_1+2\lambda_2=0$, while the second reduces to $2\lambda_1+b\lambda_2=0$.
    In particular, the rays spanned by $(2,-c)$ and $(b,-2)$ determine this change of state in the dominance regions $\cP(\lambda)$.
  \end{proof}

@@
